---
title: "Human Activity Recognition with Accelerometers"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(randomForest)
library(tidyverse)
set.seed(1234)
```

## Introduction

This project uses accelerometer data collected from multiple body locations to predict the manner in which participants performed barbell lifts. The target variable is `classe`, representing the correct or incorrect execution manner.

## Load Data

```{r load-data}
train_raw <- read.csv("pml-training.csv")
test_raw <- read.csv("pml-testing.csv")
```

## Data Cleaning

```{r clean-data}
# Remove columns with mostly NA values or empty strings
train_clean <- train_raw %>% select(where(~ mean(!is.na(.)) > 0.95))
train_clean <- train_clean %>% select_if(~ !any(grepl("[^0-9.-]", as.character(.), perl=TRUE)))
train_clean$classe <- train_raw$classe

# Drop ID or irrelevant columns
train_clean <- train_clean %>% select(-c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window), everything())
```

## Partition Data

```{r split-data}
set.seed(1234)
train_index <- createDataPartition(train_clean$classe, p = 0.7, list = FALSE)
train_set <- train_clean[train_index, ]
valid_set <- train_clean[-train_index, ]
```

## Model Training with Random Forest

```{r model-training}
ctrl <- trainControl(method = "cv", number = 5)
rf_model <- train(classe ~ ., data = train_set, method = "rf", trControl = ctrl)
```

## Evaluation

```{r eval-model}
pred_valid <- predict(rf_model, valid_set)
confusionMatrix(pred_valid, valid_set$classe)
```

## Predict Test Set

```{r predict-test}
test_clean <- test_raw %>% select(names(train_set)[names(train_set) != "classe"])
pred_test <- predict(rf_model, test_clean)
pred_test
```

## Conclusion

The Random Forest model achieved strong accuracy in cross-validation. It was then used to predict 20 test cases as required. All steps are reproducible and suitable for GitHub submission.
